03_wrangle

### 2020-08-26 analysis/03_datawrangling.Rmd
better fig size

venn.diagram(
  x = list(inc.d3_m.inc.d3DEGs,hatch_m.n2DEGs,
            inc.d9_m.inc.d9DEGs, inc.d17_m.inc.d17DEGs),
  category.names = c("Inc 3" , "Hatch" , "Inc 9", " Inc 17"),
  filename = '../figures/venn-pit.png',
  output=FALSE,
  print.mode = "raw",
  col=c("#CDCDCD", '#262625', '#959595','#959595'),
  fill = c("#CDCDCD", "#262625", "#959595", "#959595"),
  main = "Pituitary - Offspring Removal",
  sub = "Differentially expressed genes relative to internal controls"
  )

@@

# chicks
venn.diagram(
  x = list(bldg_n5DEGs, bldg_hatchDEGs, 
           bldg_earlyDEGs,bldg_extendDEGs,  bldg_n9DEGs),
  category.names = c( "N5" ,"Hatch" , "Early", " Extend", "N9"),
  filename = '../figures/venn-chicks-hyp.png',
  output=FALSE,
  print.mode = "raw",
  col=c('#3182bd', "#6baed6",  '#cbc9e2', '#6a51a3', '#08519c'),
  fill = c("#3182bd", "#6baed6", "#cbc9e2", '#6a51a3', "#08519c" ),
  main = "Hypothalamus - Nestling Care",
  sub = "Differentially expressesed genes relative to nest building controls"
  )

@@

# chicks
venn.diagram(
  x = list(bldg_inc.d3DEGs, bldg_layDEGs,  bldg_prolongDEGs,
           bldg_inc.d17DEGs, bldg_inc.d9DEGs),
  category.names = c("Inc3" , "Lay" , "Prolong", " Inc17", "Inc9"),
  filename = '../figures/venn-eggs-hyp.png',
  output=FALSE,
  print.mode = "raw",
  col=c( '#78c679', "#fed98e",  '#9e9ac8','#006837', '#31a354'),
  fill = c("#78c679", "#fed98e",  "#9e9ac8",'#006837', "#31a354"),
  main = "Hypothalamus - Incubation",
  sub = "Differentially expressesed genes relative to nest building controls"
  )

>>>>

venn.diagram(
  x = list(inc.d3_m.inc.d3DEGs,hatch_m.n2DEGs,
            inc.d9_m.inc.d9DEGs, inc.d17_m.inc.d17DEGs),
  category.names = c("Inc 3" , "Hatch" , "Inc 9", " Inc 17"),
  filename = '../figures/venn-pit.png',
  output=FALSE,
  print.mode = "raw",
  imagetype = "png",
  col=c("#CDCDCD", '#262625', '#959595','#959595'),
  fill = c("#CDCDCD", "#262625", "#959595", "#959595"),
  main = "Pituitary - Offspring Removal",
  sub = "Differentially expressed genes relative to internal controls"
  )

@@

# chicks
venn.diagram(
  x = list(bldg_n5DEGs, bldg_hatchDEGs, 
           bldg_earlyDEGs,bldg_extendDEGs,  bldg_n9DEGs),
  category.names = c( "N5" ,"Hatch" , "Early", " Extend", "N9"),
  filename = '../figures/venn-chicks-hyp.png',
  output=FALSE,
  print.mode = "raw",
  imagetype = "png",
  col=c('#3182bd', "#6baed6",  '#cbc9e2', '#6a51a3', '#08519c'),
  fill = c("#3182bd", "#6baed6", "#cbc9e2", '#6a51a3', "#08519c" ),
  main = "Hypothalamus - Nestling Care",
  sub = "Differentially expressesed genes relative to nest building controls"
  )

@@

# chicks
venn.diagram(
  x = list(bldg_inc.d3DEGs, bldg_layDEGs,  bldg_prolongDEGs,
           bldg_inc.d17DEGs, bldg_inc.d9DEGs),
  category.names = c("Inc3" , "Lay" , "Prolong", " Inc17", "Inc9"),
  filename = '../figures/venn-eggs-hyp.png',
  output=FALSE,
  print.mode = "raw",
  imagetype = "png",
  height = 1500,
	width = 1500,
  col=c( '#78c679', "#fed98e",  '#9e9ac8','#006837', '#31a354'),
  fill = c("#78c679", "#fed98e",  "#9e9ac8",'#006837', "#31a354"),
  main = "Hypothalamus - Incubation",
  sub = "Differentially expressesed genes relative to nest building controls"
  )

```
```{r}
library(cowplot)
eggshyp <- png::readPNG("../figures/venn-eggs-hyp.png")
eggshyp <- ggdraw() +  draw_image(eggshyp, scale = 1)

plot_grid(eggshyp,eggshyp, eggshyp, nrow = 1)
```
